---
title: "Linear Models"
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
library(tidyverse)
library(p8105.datasets)
theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Examples

AirBnB

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group,
         neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)

```

Fit a model for price as an outcome 

```{r}

fit = lm(price ~ stars + boro, data = nyc_airbnb)

```

Look at summaries


```{r}
summary(fit)
summary(fit)$coef
coef(fit)
# fitted.values(fit)
```

Look at better summaries...

```{r}

fit %>% 
  broom::tidy()

fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)

```

Look at other summaries...
```{r}
fit %>% 
  broom::glance()

fit %>% 
  broom::glance() %>% 
  select(r.squared, adj.r.squared)
```

Be carefu with factor order...

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(boro = fct_infreq(boro),  # in order of frequency
         room_type = fct_infreq(room_type))

fit = lm(price ~ stars + boro, data = nyc_airbnb)

fit %>% 
  broom::tidy()
```


## Diagnostics

Add residuals to dataset

```{r}
modelr::add_residuals(nyc_airbnb, fit)

modelr::add_predictions(nyc_airbnb, fit)


modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) + geom_boxplot()

modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) + geom_point()

nyc_airbnb %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = stars, y = pred, color = boro)) + geom_point()

```


## Testing

```{r}
fit %>% 
  broom::tidy()
```

Compare nested models
```{r}
fit_null = lm(price ~ stars + boro, data = nyc_airbnb)
fit_alt = lm(price ~ stars + boro + room_type, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()

```


### Nested data

```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

```

Nest dataset and then fit model...(stratified analysis)

```{r}
nest_lm_res =
  nyc_airbnb %>% 
  group_by(boro) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```


Only neighborhoods in Manhattan

```{r}
manhattan_airbnb =
  nyc_airbnb %>% 
  filter(boro == "Manhattan")

manhattan_nest_lm_res =
  manhattan_airbnb %>% 
  group_by(neighborhood) %>% 
  nest() %>% 
  mutate(models = map(data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest()
```

View some results...
differences among room types

```{r}
manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```


Mixed model with neighborhood-level random intercepts and random slopes for room type 
```{r}
#manhattan_airbnb %>% 
 # lme4::lmer(price ~ stars + room_type + (1 + room_type | neighborhood), data = .) %>% 
  # broom::tidy()
```


## Binary Outcomes

```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(resolved = as.numeric(disposition == "Closed by arrest"),
         victim_age = as.numeric(victim_age),
         victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)

```

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, 
      data = ., 
      family = binomial()) 
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)


fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = boot::inv.logit(estimate)) %>%
  knitr::kable(digits = 3)
```

```{r}
baltimore_df %>% 
  modelr::add_predictions(fit_logistic) %>% 
  mutate(fitted_prob = boot::inv.logit(pred))
```

```{r}
baltimore_df %>% 
  ggplot(aes(x = victim_age, y = resolved)) +
    geom_point() + geom_smooth()
```

